Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-11-11 ms.tex
Kite referece, updated authors, affiliations and figure sizes to match arXiv version.

\author{E. Schlawin}
\affiliation{Steward Observatory, Tucson AZ 85721}

@@

\author{Hajima Kawahara}
\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}

@@

\author{Elizabeth Green}
\affiliation{Steward Observatory, Tucson AZ 85721}

\author{Benjamin V. Rackham}
\affiliation{Steward Observatory, Tucson AZ 85721}

@@

\begin{deluxetable}{lrrrr}
\tablecaption{List of photometric observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Airmass} &
\colhead{Seeing} &
\colhead{Amplitude, $A$} \\
\colhead{UT} & & & (\arcsec) & \\
 }
\startdata
2016 Jun 10 & Cloudy	& \nodata & \nodata &  \nodata \\
2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	& 1.4 &	0.70 $\pm$ 0.18\\
2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1.63	& 1.2 &	0.78 $\pm$ 0.14 \\
2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.2 & 	1.33 $\pm$ 0.14 \\
2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 1.4 & 	2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper telescope.
The seeing is expressed as the median FWHM for the night in arcseconds.}
\end{deluxetable}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.49\textwidth]{figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of \added{the} Mont4K \added{imager}.
{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
The reference stars were chosen to have similar count levels as \shStar.
}\label{fig:refStars}
\end{centering}
\end{figure}

@@

In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
\added{We also show the formal false alarm levels of $5 \times 10^{-2}$ and $10^{-4}$ for the periodograms.}
\deleted{The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.}
The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
The second principal component's periodogram has a strong peak at 491 days.
This singly-peaked periodogram \deleted{(other than the 0.654 day sampling period)} implies that PC$_2$ is nearly sinusoidal.
As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.
It is also possible that red noise such as 1/$f$ noise contributes to these long term oscillations.

@@

\begin{deluxetable}{cccccccc}
\tablecaption{List of Spectroscopic Observations}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 & 2013 Jun 22 & 12:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 & 2013 Jun 22 & 13:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 05:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 06:19 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 07:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 08:15 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 09:17 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 05:34 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 06:17 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 07:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 08:31 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 09:14 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
\end{deluxetable}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{Thanks to Ben Weiner for some useful discussion on high resolution spectroscopy.
This work was supported by the Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}

>>>>

\author[0000-0001-8291-6490]{Everett Schlawin}
\affiliation{Steward Observatory, Tucson AZ 85721}

@@

\author{Hajime Kawahara}
\affiliation{Department of Earth and Planetary Science, The University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Research Center for the Early Universe, School of Science, The University of Tokyo, Tokyo 113-0033, Japan}

@@

\author{Elizabeth M. Green}
\affiliation{Steward Observatory, Tucson AZ 85721}

\author[0000-0002-3627-1676]{Benjamin V. Rackham}
\affiliation{Steward Observatory, Tucson AZ 85721}
\affiliation{Earths in Other Solar Systems Team, NASA Nexus for Exoplanet System Science.}

@@

\begin{deluxetable*}{lrrrr}
\tablecaption{List of photometric observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Weather} &
\colhead{Airmass} &
\colhead{Seeing} &
\colhead{Amplitude, $A$} \\
\colhead{UT} & & & (\arcsec) & \\
 }
\startdata
2016 Jun 10 & Cloudy	& \nodata & \nodata &  \nodata \\
2016 Jun 12 & Clear 	& 1.29 $\rightarrow$ 1.06 $\rightarrow$ 1.10	& 1.3 &	0.94 $\pm$ 0.16 \\
2016 Jun 14 & Clear 	& 1.47 $\rightarrow$ 1.06 $\rightarrow$ 1.12	& 1.4 &	0.70 $\pm$ 0.18\\
2016 Jul 12 & Clear 		& 1.19 $\rightarrow$ 1.06 $\rightarrow$ 1.63	& 1.2 &	0.78 $\pm$ 0.14 \\
2016 Jul 14 & Mostly clear	& 1.24 $\rightarrow$ 1.06 $\rightarrow$ 1.55 & 1.2 & 	1.33 $\pm$ 0.14 \\
2016 Jul 16 & Clear 		& 1.36 $\rightarrow$ 1.06 $\rightarrow$ 1.26	& 1.4 & 	2.14 $\pm$ 0.19 \\
\enddata
\tablenotetext{}{Summary of the attempted photometric observations of \shStar\ with the 61-inch Kuiper telescope.
The seeing is expressed as the median FWHM for the night in arcseconds.}
\end{deluxetable*}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.49\textwidth]{figure_index_152.pdf}
\includegraphics[width=0.49\textwidth]{stamps_kic1255_UT2016_07_14.pdf}
\caption{{\it Left:} \shStar\ (src) and reference stars (numbered) used on UT 2016-07-14 are shown over the full 9.8\arcmin $\times$ 9.8\arcmin\ Field of View of \added{the} Mont4K \added{imager}.
{\it Right:} Postage stamp zoom-ins for the source and reference stars show the point spread functions for each star.
The reference stars were chosen to have similar count levels as \shStar.
}\label{fig:refStars}
\end{centering}
\end{figure*}

@@

In Figure \ref{fig:ampPeriodogram} we show the periodogram of the principal components.
\added{We also show the formal false alarm levels of $5 \times 10^{-2}$ and $10^{-4}$ for the periodograms.}
\deleted{The peaks at 0.654 days in both the first and second principal components are the same as the orbital period, which determines the sampling cadence of the time series of amplitudes and principal components.}
The first component, corresponding to the transit depth, has peaks at 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
The second principal component's periodogram has a strong peak at 491 days.
This singly-peaked periodogram \deleted{(other than the 0.654 day sampling period)} implies that PC$_2$ is nearly sinusoidal.
As shown in Figure \ref{fig:pcaVectorsComp}, the second principal component resembles models with larger dust grains, so the dust grain sizes could be evolving on long-term 491-day timescales.
This is much longer than the dynamical and sublimation times of the system, so there is no obvious mechanism for the dust grain size evolution.
\added{However, this timescale is close to the overturning timescale for a magma pool \citep{kite2016atmInteriorExchange}, which could control the source of metal rich vapor that creates grains.} 
It is also possible that red noise such as 1/$f$ noise contributes to these long term oscillations.

@@

\begin{deluxetable*}{cccccccc}
\tablecaption{List of Spectroscopic Observations}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 & 2013 Jun 22 & 12:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 & 2013 Jun 22 & 13:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 05:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 06:19 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 07:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 08:15 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 09:17 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 05:34 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 06:17 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 07:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 08:31 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 09:14 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
\end{deluxetable*}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
The authors thank to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for E Schlawin is provided by NASA Goddard Spaceflight Center.
\replaced{The authors thank Benjamin Rackham for providing an estimate of the transit light source effect for a K4 V star and for helpful comments from Saul Rappaport.}{The authors thank Saul Rappaport for helpful comments.} % Now Ben is a coauthor
\added{Thanks to Ben Weiner for some useful discussion on high resolution spectroscopy.
This work was supported by the Japan Society for Promotion of Science (JSPS) KAKENHI Grant Number JP16K17660.
Support for this work was provided by NASA through Hubble Fellowship grant HST-HF2-51399.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.}
\added{This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France. The original description of the VizieR service was published in \citet{ochsenbein2000vizieR}.
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
This publication makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.}
The results reported herein benefited from collaborations and/or information exchange within NASA?s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA?s Science Mission Directorate.
